---
title: "Data Products Pitch: Submarine Hunt"
author: "Marvin J. Rich"
date: "March 9, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Objective
The purpose of this pitch is to illustrate the integration of graphics, plotting technique, and user interaction in a Shiny App. These capabilities are utilized in a Submarine Hunt game that integrates these aspects as following:   

- Graphics: icons to provide visual effects
- Plotting Technique: Plotting icons manipulated in shiny server code.
- Interaction: Shiny widgets to provide user input and results.  

## The Game

- User attempts to hit submarines rendered on a radar screen
- Radar screen depicts coordinates for target selection
- Shiny widgets provide an aiming and firing mechanism to the user
- Input is processed when a fire button is selected
- Radar screen provides feedback on firing results (hit/miss)

## Game Design Techniques

- Hit/Miss calculations based on input x,y firing coordinates
- Hit: x,y firing coordinates match one of three submarine positions
- Miss: x,y firing coordinates miss all three submarine positions
- sliderInput() function used to select x,y firing coordinates
- submitButton() used to fire and reflect hit status
- Free web icons used for submarine,splash, & explosion respectively
- Overlay icons to get combination effects (i.e. explosion+submarine)
- Used qplot annotation_raster() function to size and place icon on coordinate (x,y)
- Hit Display: splash and explosion displayed over existing submarine 
- Miss Display: splash displayed at missed x,y position
- Can show/hide submarine locations on screen via checkboxInput()

## Submarine Hunt App Output Example  

Hit = Explosion (x=7,y=7), Miss = Splash (x=3,y=3):

```{r echo = FALSE,message=FALSE,warning=FALSE}
library(png)
library(ggplot2)


img1 <- readPNG("bship.png")
img2 <- readPNG("boom.png")
img3 <- readPNG("splash.png")

set.seed(7774)
  
s <- data.frame(x=sample(1:10,size=3,replace=FALSE),
                y=sample(1:10,size=3,replace=FALSE),
                hit = FALSE)

x1 <- s[,]$x-0.7
x2 <- s[,]$x+0.7
y1 <- s[,]$y-0.7
y2 <- s[,]$y+0.7
      
#-- Plot Radar       
g <- qplot( 1:10,1:10,geom="blank") + 
          scale_x_continuous(name="RadarX-Coordinate",limits=c(1,10),
                             breaks=seq(1,10,1))+
          scale_y_continuous(name="RadarY-Coordinate",limits=c(1,10),
                             breaks=seq(1,10,1))+
        
          theme(panel.background = element_rect(fill="lightblue",
                                                colour = "navy"))+
          geom_point(alpha=0.01)
    
     
      
#-- Plot Submarines        
for (i in 1:3) {
  g <- g + annotation_raster(img1,xmin=x1[i],xmax=x2[i],
                             ymin=y1[i],ymax=y2[i]) 
}

x1a <- 7-0.7
x1b <- 7+0.7
y1a <- 7-0.7
y1b <- 7+0.7

#-- hit example
g <- g + annotation_raster(img1,xmin=x1a,xmax=x1b,ymin=y1a,ymax=y1b)
g <- g + annotation_raster(img3,xmin=x1a,xmax=x1b,ymin=y1a,ymax=y1b)
g <- g + annotation_raster(img2,xmin=x1a,xmax=x1b,ymin=y1a,ymax=y1b)

x1a <- 3-0.7
x1b <- 3+0.7
y1a <- 3-0.7
y1b <- 3+0.7
                          
#-- miss example
g <- g + annotation_raster(img3,xmin=x1a,xmax=x1b,ymin=y1a,ymax=y1b)

#-- show ouput                    
g   
 
```



